%-----------------------------------------------------------------------------------------------------------------------------------------------%
%   The MIT License (MIT)
%
%   Copyright (c) 2021 Jitin Nair
%
%   Permission is hereby granted, free of charge, to any person obtaining a copy
%   of this software and associated documentation files (the "Software"), to deal
%   in the Software without restriction, including without limitation the rights
%   to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%   copies of the Software, and to permit persons to whom the Software is
%   furnished to do so, subject to the following conditions:
%   
%   THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%   IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%   FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%   AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%   LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%   OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%   THE SOFTWARE.
%   
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%   DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%   FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%   PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip}
\usepackage{changepage}

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}               
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }



%----------------------------------------------------------------------------------------
%   BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%   TITLE
%----------------------------------------------------------------------------------------

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Raymond Liu} \\[7.5pt]
\href{https://github.com/rl27}{\raisebox{-0.05\height}\faGithub\ rl27} \ $|$ \ 
\href{https://linkedin.com/in/raymondzl}{\raisebox{-0.05\height}\faLinkedin\ raymondzl} \ $|$ \ 
\href{https://rl27.github.io}{\raisebox{-0.05\height}\faGlobe \ rl27.github.io} \ $|$ \ 
\href{mailto:liur@seas.harvard.edu}{\raisebox{-0.05\height}\faEnvelope \ liur@seas.harvard.edu} \
% $|$ \ 
% \href{tel:5416020508}{\raisebox{-0.05\height}\faMobile \ (541) 602-0508} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%   EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{adjustwidth}{0.7em}{0pt}

\begin{joblong}{Harvard University}{2024 – Present}
\item PhD in Computer Science (GPA: 4.0/4.0)
\item Funded by the NSF GRFP
\end{joblong}

\vspace{-3pt}
\begin{joblong}{Princeton University}{2019 – 2023}
\item BSE in Computer Science (GPA: 3.9/4.0)
\item Minor in Statistics and Machine Learning
% \item Relevant courses: Computer Vision, NLP, Mathematics for Machine Learning, \newline Algorithms and Data Structures, Statistics \& Data Analysis, Computer Architecture
\end{joblong}

% \begin{tabularx}{\linewidth}{@{}p{6.2in} X@{}} 
% \textbf{Harvard University} & \hfill \normalsize 2024 - Present \\
% \hspace{1em}\textit{PhD in Computer Science} \\

% \vspace{-4pt}
% \textbf{Princeton University} & \hfill 2019 - 2023 \\
% \hspace{1em}\textit{B.S.E. in Computer Science (GPA: 3.9/4.0)} \\
% \hspace{1em}\textit{Certificate in Statistics and Machine Learning} \\
% \hspace{1em}Relevant courses: Computer Vision, NLP, Mathematics for Machine Learning, Algorithms and Data Structures, Statistics \& Data Analysis \\

% \vspace{-4pt}
% \textbf{Crescent Valley High School} & \hfill 2016 - 2019 \\
% \hspace{1em}\textit{Valedictorian (GPA: 4.0/4.0)} \\
% \end{tabularx}

\end{adjustwidth}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
\vspace{-10pt}
\section{Publications}

\textbf{Raymond Liu} and Patrick Slade. Improving navigation for people with blindness using an AI-driven smartphone application and personalized audio guidance. \textit{Under review at Nature Biomedical Engineering}, 2025

\textbf{Raymond Liu}, Ava Lakmazaheri, Estelle Richard, Louis Marchand, Elena Glassman, and Patrick Slade. Training methods for spatial audio feedback with human-robot interaction. \textit{In preparation for Nature Human Behaviour}, 2026

Robin Pan, \textbf{Raymond Liu}, Daniel Fang, Rosa Wu, and Adelina Andrei. Elbow-based MoE Routing: A Training-Free Inference Time Plugin for Expert Selection. \textit{Under review as a workshop paper at ICLR}, 2026

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Experience
\vspace{-2pt}
\section{Work Experience}
\begin{adjustwidth}{0.7em}{0pt}

\begin{joblong}{Visiting Researcher at Harvard Ability Lab}{July 2023 – Aug. 2024}
\item Developing a smartphone-based navigation assistant for people who are blind or visually impaired.
\item For this work, we received funding from the Amazon Greater Boston Tech Initiative (\$50k) and the Harvard GRID Accelerator (\$100k).
\end{joblong}

\begin{joblong}{Software Engineering Intern at Amazon}{May 2022 – Aug. 2022}
\item Developed, tested, and optimized an API in Java to send parallelized batch requests to Elasticsearch and greatly speed up workflows.
\end{joblong}

\begin{joblong}{Teaching Assistant at Princeton University}{Sept. 2021 – May 2023}
\item TA for \href{https://www.cs.princeton.edu/courses/archive/fall21/cos340/}{COS340 – Reasoning about Computation}
\item Guided students during regular office hours; graded and provided feedback for assignments and exams.
\item Covered mathematical and theoretical topics in computer science – combinatorics, probability, graph theory, NP-completeness, and cryptography.
\end{joblong}

\begin{joblong}{Research Project at Princeton University}{June 2021 – Feb. 2022}
\item Joined the Laboratory for Intelligent Probabilistic Systems.
\item Developed a system for visualizing generative models in 3D hyperbolic space. Created a model and projection of 3D hyperbolic space using OpenGL and connected the model with a model for generating correlated images based on geodesic distance.
\end{joblong}

\begin{joblong}{Research Assistant at Princeton University}{June 2020 – Aug. 2020}
\item Joined the Princeton Vision \& Learning Lab to work on a visual learning project on optical flow.
\item Developed and optimized a system for collecting human-annotated images and predicting ground truth optical flow from annotation pairs.
\end{joblong}

\begin{joblong}{Computer Graphics Internship at Oregon State University}{June 2018 – Aug. 2018}
\item Designed a ray tracer / image renderer from scratch using C++. Tested and implemented a variety of methods to increase image realism and accelerate rendering speed.
\end{joblong}

\end{adjustwidth}

% Awards
\section{Honors, Awards, and Achievements}
\begin{adjustwidth}{0.7em}{0pt}

\begin{jobshort}{NSF Graduate Research Fellowship Awardee}{Apr. 2024}
\end{jobshort}
\begin{joblong}{Harvard GRID Accelerator Awardee}{Feb. 2024}
    \item Received \$100k in funding for our proposal, “Navigation assistant for people with impaired vision or blindness.” 
\end{joblong}
\begin{joblong}{Amazon Greater Boston Tech Initiative Awardee}{Dec. 2023}
    \item Received \$50k in funding for our proposal, “Curriculum for developing a robotic navigation assistant for people with visual impairment.” 
\end{joblong}
\begin{jobshort}{NSF Graduate Research Fellowship Honorable Mention}{Mar. 2023}
\end{jobshort}
\begin{joblong}{USA Junior Mathematical Olympiad Qualifier}{Apr. 2018}
    \item One of 156 qualifiers nationwide.
\end{joblong}
\begin{joblong}{American Invitational Mathematics Examination (AIME) Qualifier}{2016, 2017, 2018}
    \item The top 2.5\% of participants in the AMC 10 exam qualify for the AIME.
\end{joblong}
\begin{jobshort}{Oregon Invitational Mathematics Tournament - 3rd Place (Team Event)}{May 2018}
\end{jobshort}
\begin{jobshort}{Oregon Invitational Mathematics Tournament - 4th Place (Calculus)}{May 2017}
\end{jobshort}
\begin{jobshort}{Intel Northwest Science Expo (NWSE) Finalist}{Apr. 2017}
\end{jobshort}
\begin{jobshort}{IEEE Excellence in Computer Science Award at Intel NWSE}{Apr. 2017}
\end{jobshort}
\begin{jobshort}{Central Western Oregon Science Expo (CWOSE) Finalist}{Feb. 2017}
\end{jobshort}
\begin{jobshort}{Yale Science and Engineering Award in Computer Science at CWOSE}{Feb. 2017}
\end{jobshort}
\end{adjustwidth}

%----------------------------------------------------------------------------------------
%   PUBLICATIONS
%----------------------------------------------------------------------------------------
% \section{Publications}
% \begin{refsection}[citations.bib]
% \nocite{*}
% \printbibliography[heading=none]
% \end{refsection}

%----------------------------------------------------------------------------------------
%   SKILLS
%----------------------------------------------------------------------------------------
% \section{Skills}
% \begin{tabularx}{\linewidth}{@{}l X@{}}
% Languages &  \normalsize{C++, C, C\#, Python, Java, JavaScript, HTML, CSS, OCaml}\\
% Frameworks \& Tools  &  \normalsize{Git, LaTeX, PyTorch, NumPy, Matplotlib, jQuery, Bootstrap, Flask}\\  
% \end{tabularx}

\vfill
\center{\footnotesize Last updated: \today}

\end{document}